### 2016-09-06 R/ITHIM.Rmd
Updated ITHIM.Rmd

reformatData2 <- function(data){
foo <- matrix(unlist(data), nrow = 7, ncol = 2)
foo <- rbind( c(0.1, 0.1), foo)
dimnames(foo) <- list(paste0("ageClass",1:8), c("F","M"))
return(foo[,c("M","F")])
}

@@

  ITHIM.national <- createITHIM(vision = "baseline", region = "national")
  ITHIM.national <- updateITHIM(ITHIM.national, "muNonTravel", muNonTravel)
  ITHIM.national <- updateITHIM(ITHIM.national, "muwt", muwtNational)
  ITHIM.national <- updateITHIM(ITHIM.national, "muct", muctNational)
  ITHIM.national <- updateITHIM(ITHIM.national, "Rwt", RwtNational)
  ITHIM.national <- updateITHIM(ITHIM.national, "Rct", RctNational)
  DALYs <- lapply(ITHIMList, sumDALY, ITHIM.baseline = ITHIM.national)
  DALYs <- data.frame(HHS = names(DALYs), muNonTravel = muNonTravel, DALY = unlist(DALYs))
  DALYsTotal <- rbind(DALYsTotal, DALYs)
}
}else{
DALYsTotal <- readRDS(file = "./data/DALYsTotal.rds")
}
p <- ggplot(DALYsTotal, aes(x = muNonTravel, y = DALY, colour = HHS))
p  + geom_line() + theme_bw() + scale_x_discrete(name="Non-Travel METs mean") + scale_y_continuous(name="Change in DALY (National)") + facet_grid(. ~ HHS)
```

>>>>

@@

  ITHIM.national <- createITHIM(vision = "baseline", region = "national")
  ITHIM.national <- updateITHIM(ITHIM.national, "muNonTravel", muNonTravel)
  ITHIM.national <- updateITHIM(ITHIM.national, "muwt", muwtNational)
  ITHIM.national <- updateITHIM(ITHIM.national, "muct", muctNational)
  ITHIM.national <- updateITHIM(ITHIM.national, "Rwt", RwtNational)
  ITHIM.national <- updateITHIM(ITHIM.national, "Rct", RctNational)
  DALYs <- lapply(ITHIMList, sumDALY, ITHIM.baseline = ITHIM.national)
  DALYs <- data.frame(HHS = names(DALYs), muNonTravel = muNonTravel, DALY = unlist(DALYs))
  DALYsTotal <- rbind(DALYsTotal, DALYs)
}
}else{
DALYsTotal <- readRDS(file = "./data/DALYsTotal.rds")
}
p <- ggplot(DALYsTotal, aes(x = muNonTravel, y = DALY, colour = HHS))
p  + geom_line() + theme_bw() + scale_x_continuous(name="Non-Travel METs mean") + scale_y_continuous(name="Change in DALY (National)") + facet_grid(. ~ HHS)
```
